\section{Using Blockchains as a replacement for Certificate Authorities}

\subsection{Problem summary}
There are currently two Public Key Infrastructures in place: Certificate Authorities and Web of Trust.

The Certificate Authority system relies on the trust placed upon a central Certificate Authority.
This trust can easily be misplaced, as the hacking of Diginotar has shown and the Trustwave incident.
The central point also introduces a natural single point of failure and a high value target.
The revelations of Snowden also further makes it questionable if an organisation is not forced into creating backdoors for intelligence agencies.

The Web of Trust system is a decentralized approach, but still relies on meeting in person and trusting nodes in the network.
It is also difficult to join the web as a newcomer.
So it has drawbacks of its own.

\subsection{Directions of research}

A possible solution is to adept the power of blockchain to solve this problem.
Certifications can be moved towards the blockchain and can be verified by the network.
Only two papers were found in the preliminary research on the topic
and no real life prototype is currently working.

One of the problem with the solution is that the identity has to be asserted of a newcomer without a face to face meeting.
For example, the current PKI rely on a real life meeting or only on a prove of ownership by publishing a specific HTML file to a server.
For a system to replace the current PKI infrastructure this has to be achieved,
or cyber squatting would become a problem.
This could also possibly be a direction of research; how can a distributed network to assert someone's identity.

\subsection{Threats}
The subject is very interesting, but also very new.
This leads to the question if a substantial prototype can be achieved during the thesis.
The threat is that the thesis would only result in a theoretical contribution.

\subsection{Related work}
Namecoin is an adaptation of Bitcoin to provide DNS services \cite{Namecoin}.
Building upon Namecoin, a proposal named Certcoin has be done that provides PKI infrastructure\cite{fromknecht2014certcoin}.
Further work has been published about a building a decentralized anonymous credential system\cite{garmandecentralized}

The research in related work only turned up two papers and discussion on internet fora about the subject.
That gives some leads to potential problems in the solution.
Certcoin comes the closest to a real working protocol,
but it is for now only a proposal. 
Collaboration during the thesis would be a very interesting opportunity.

There is extensive work done on Bitcoin itself.

