\section{Tamper-proof interaction histories}

\subsection*{Problem summary}
There is a need for a interaction history, from which a reputation or a level of trust can be deduced for a entity, when dealing with unknown entities in a network.
This can be solved with a range of different data structures.
One of the main data structure that has been gathering significant attention and has shown a huge amount of growth in use is the blockchain.
The blockchain is the fundamental concept where Bitcoin builds upon.
Other data structures commonly have the problem of having the risk that the history could have been tampered with.
This is not possible with blockchains to a certain probability.

But the problem with the blockchain is that even though it is now scalable enough for Bitcoin,
it will grow to become a very large datastructure and it is limited per design to be able to only handle 7 transactions per second.
The large data structure limits the range of devices that will be able to handle the blockchain in the future.
The limitation of transactions of second will make it never to be able to replace a system with much more transactions per second,
for example the banking system.

\subsection*{Directions of research}
A direction of research would be to implement a prototype of DoubleEntry.
This is an improvement of the blockchain concept.
The history is distributed over several chains. 
Interactions bind together chains.
This solves the problem of one huge data structure limiting the devices that can handle the chain.
It is in a sense an expanding acyclic graph.

\subsection*{Threats}
A very novel field proposing an improvement on the blockchain idea which itself is very new and a subject of research.
The proposal of the subject was done for a grant for a post doc employee.
So the threat is that the subject is too extensive to come up with something meaningful within a Master Thesis.

\subsection*{Related work}
The direction of research was done in a grant proposal by Dr. Ir. Pouwelse.
There is a vast amount of papers proposing improvements of Bitcoin.
Examining these on related work would be worth a whole literature study of 10 ects.
Because the general concept is clear to the author through explanations of Dr. Ir. Pouwelse,
no further research is done at this time for related work,
except for a few superficial queries to scholar.google.com.
